### 2019-06-06 2-Chapters/1-Chapter/chapter1.tex
Lots of small changes
- added a title/author etc in metadata
- cleaner small proof with an environment

\paragraph{Copyright notice.}
%
This document and the additional resources required to compile it (including \LaTeX{} code, Python snippets, images etc)
are \href{https://github.com/Naereen/phd-thesis/}{publicly published},
online at \href{https://github.com/Naereen/phd-thesis/}{\texttt{GitHub.com/Naereen/phd-thesis/}},
under the terms of the open-source \href{https://lbesson.mit-license.org/}{\emph{MIT License}}.

>>>>

\paragraph{Copyright notice.}
%
This document and the additional resources required to compile it (including \LaTeX{} code, Python snippets, images etc)
are \href{https://github.com/Naereen/phd-thesis/}{publicly published},
under the terms of the open-source \href{https://lbesson.mit-license.org/}{\emph{MIT License}},
online at \href{https://github.com/Naereen/phd-thesis/}{\texttt{GitHub.com/Naereen/phd-thesis/}},

### 2019-06-06 2-Chapters/2-Chapter/IEEE_WCNC_2018.git/IEEE_WCNC__2018__Paper__Lilian_Besson__07-17.tex
Lots of small changes
- added a title/author etc in metadata
- cleaner small proof with an environment

The reward estimate is unbiased in the following sense. If one had access to the samples $Y_{k,t+1}$ for all arms $k$, the reward incurred by algorithm $a$ at time $t+1$ would be $r^a(t+1) = Y_{A_a(t+1),t+1}$.
But we are not in the full information setting (see \cite{CesaLugosi06}), but in the bandit setting, so only one of the samples $Y_{k,t+1}$ can be observed, $r(t)=Y_{A(t+1),t+1}$.
This quantity can only be observed for those algorithms $a$ for which $A_{a}^{t+1}=A(t+1)$.
However, by dividing by the probability of observing this recommendation, one obtains an unbiased estimate of $r^a(t+1)$. More precisely, if we define the estimate by
\begin{equation}
	\widehat{r^a}(t+1) = \frac{Y_{A_a(t+1),t+1}}{p_{A_a(t+1)}^{t+1}} \indic(A_a(t+1) = A(t+1))
\end{equation}
satisfies $\E_{\cO_t}[\widehat{r^a}(t+1) | \cO_t] = Y_{A_a(t+1),t+1}$, for all $a$, where the expectation is taken conditionally to the history of observations up to round $t$, $\cO_t$.
%
Observe that $\widehat{r^a}(t+1) = 0$ for all algorithms $a$ such that $A_a(t+1) \neq A(t+1)$.

>>>>

The reward estimate is unbiased in the following sense. If one had access to the samples $Y_{k,t+1}$ for all arms $k$, the reward incurred by algorithm $a$ at time $t+1$ would be $r^a(t+1) = Y_{A_a(t+1),t+1}$.
But we are not in the full information setting (see \cite{CesaLugosi06}), but in the bandit setting, so only one of the samples $Y_{k,t+1}$ can be observed, $r(t)=Y_{A(t+1),t+1}$.
This quantity can only be observed for those algorithms $a$ for which $A_{a}^{t+1}=A(t+1)$.
However, by dividing by the probability of observing this recommendation, one obtains an unbiased estimate of $r^a(t+1)$. More precisely, if we define the estimate by
\begin{equation}
	\widehat{r^a}(t+1) = \frac{Y_{A_a(t+1),t+1}}{p_{A_a(t+1)}^{t+1}} \indic(A_a(t+1) = A(t+1))
\end{equation}
satisfies $\E_{O_t}[\widehat{r^a}(t+1) | O_t] = Y_{A_a(t+1),t+1}$, for all $a$, where the expectation is taken conditionally to the history of observations up to round $t$, $O_t$.
%
Observe that $\widehat{r^a}(t+1) = 0$ for all algorithms $a$ such that $A_a(t+1) \neq A(t+1)$.
